Occurrence and transmission potential of asymptomatic and pre-symptomatic SARS-CoV-2 infections: a living systematic review and meta-analysis

### 2021-10-27 Manuscript_draft.Rmd
updated 2.1 plot

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

@@

q2_1_asymp <- metabin(event.e = Ee,
                      n.e = Ne,
                      event.c = Ec,
                      n.c = Nc, 
                      data = q2_1_df,
                      studlab = author_1,
                      prediction = TRUE,
                      sm = "RR",
                      method = "MH",
                      MH.exact = TRUE, 
                      byvar = group, 
                      comb.random = TRUE,
                      comb.fixed = FALSE)
q2_1_asymp

@@

forest(q2_1_asymp, sortvar = (1/(sqrt(seTE))), overall = FALSE)

png(file = 'forest_meta_Q2_1.png', width=25,height=13, res=600, units="cm")

forest(q2_1_asymp, sortvar = (1/(sqrt(seTE))), overall = FALSE)

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

@@

q2_1_asymp <- metabin(event.e = Ee,
                      n.e = Ne,
                      event.c = Ec,
                      n.c = Nc, 
                      data = q2_1_df,
                      studlab = author_1,
                      prediction = TRUE,
                      sm = "RR",
                      method = "MH",
                      MH.exact = TRUE, 
                      byvar = group,
                      comb.random = TRUE,
                      comb.fixed = FALSE, 
                      label.e = "",
                      label.c = "Symptomatic")
q2_1_asymp

@@

forest(q2_1_asymp, sortvar = (1/(sqrt(seTE))), overall = FALSE,
       overall.hetstat = FALSE,
       leftlabs = c(NA, "      E", "      N", "            E", "        N"))
